\section{Literature Review}
\label{sec:literature_review}

\subsection{Joystick Mechanisms}
\label{sub:joystick_mechanisms}

% subsection joystick_mechanisms (end)

\subsection{Haptic Feedback Technologies}
\label{sub:haptic_feedback_technologies}

% subsection haptic_feedback_technologies (end)

\subsection{Market Research / Patented Technologies}
\label{sub:market_research_patented_technologies}

% subsection market_research_patented_technologies (end)

\section{Literature Review}
\label{sec:literature_review}

\subsection{Joystick Mechanisms}
\label{sub:joystick_mechanisms}
Different types of joysticks there are around, how do they achieve 1,2 or 3 degrees of freedom. How do they feel? (Stiff or low inertia)

What sorts of controllers are there?

1) flight controllers\\
2)games controllers, but then even then different types\\
    Nintendo wii; Playstation; continuous vs button.\\
    How do they work? Accelerometers, potentiometers, encoders, MR sensors\\


Then throw in an analysis of what is good about each, bad about each, relink in to our constraints and show the direction that would be good for us to head in.

% subsection joystick_mechanisms(end)

\subsection{Haptic Technologies}
\label{sub:market_research}
Haptic Cow, Virtual reality, gaming devices,  and geomagic interfaces used for 3D designing. At the moment the mechatronics department is using a piece like this but it is very expensive and large -> therefore leading onto the requirement of something smaller with more basic functionalities.
Then onto research papers and patented designs of joystick mechanisms.
Input MR haematoglogical paper which we based our gimbal mechanism on.
Input awesome paper medler found with springs. (explain reasons why this may be a little too optimistic for us to produce with budget limitations / can’t copy patented design)
3) Others that are similar to ours, other projects\\
    Cool paper with the patent. Hapkit ; two papers I have bookmarked; first one we found with MR, but same mechanism\\
4) Professional ones;\\
    Omni controller; Da vinci controller\\

% subsection market_research(end)

% section literature_review (end)